\newpage
\section{The package}
The package is defined as the collection of functions (or `methods') that are part of this software. The methods are divided up in several categories:
\begin{itemize}
\item[\emph{import/output (IO)}]: Data Input/Output functions
\item[\emph{correct}]: Correction of the data, for example abberrations.
\item[\emph{convert}]: Conversion of the corrected data to other variables (signals)
\item[\emph{filter}]: The formation of filters that view only parts of the data
\item[\emph{plot}]: Show histograms of many kinds, and other graphics tools
\item[\emph{calibrate}]: Methods to verify the conversion
\item[\emph{macros}]: Meta-functions that automize the treatment and analysis of (multiple) experiments.
\item[\emph{fit}]: Methods to characterize histograms from models.
\item[\emph{theory}]: Methods to visualize or use (statistical) models.
\item[\emph{general}]: General MATLAB functions used in different places in the package.
\end{itemize}



\input{package_IO}
\input{package_correct}
\input{package_convert}
\input{package_filter}
\input{package_plot}
\input{package_calibrate}
\input{package_general}

\lstset{language=MATLAB}
\begin{lstlisting}
% Example of MATLAB codes/functions
[input1, input2] = function test(input1, input2)
\end{lstlisting}

\if
% Remarks from meeting Shabnam and Noelle 17th of september:
-make TOF to m2q not only by clicking, also by typing numbers.
Make it possible to look at the corresponding NEXAFS/total ion yield spectra also
think about the best way of determining the center of detection, which is now done by eye.
make it possible to subtract background for the converted energies from an off-resonance measurement
make it possible to calculate the beta-parameter of only a certain range of kinetic energy releases.
store all the converted values so that it can be used later.
PEPIPICO plots in m/q units instead of TOF.
don't do the m/q labeling automatically; it is best to do this manually.
combining events from different measurements is very useful. maybe also selecting a certain KE from a measurement and saving that as a separate measurement?
maybe make it possible to look at branching ratio's of different measurements?
Could the beta-parameter be determined when only part of the detector region is used?
make binsize user-adjustable
make it possible to histogram any variable against another. Maybe; define binsize for every signal.
look up how to print horizontal lines in text.
\fi
